Untitled

### 2017-02-16 Code/plot_age_standardardized_mortality_trends.Rmd

 data.sub <- subset(mortality.rates, sex == sex_i & COD == cod)
 test <- ggplot(data.sub, 
                aes(y = age.std.mortality.rate_med, x = year)) + 
      geom_vline(aes(xintercept = 1983), col = "#636363", lty = 3) +
      geom_vline(aes(xintercept = 1993), col = "#636363", lty = 3) +
      geom_ribbon(aes(ymin = age.std.mortality.rate_LCL, ymax = age.std.mortality.rate_UCL, group = race, fill = Census_Division), col = NA, alpha = 0.5) +
      geom_line(aes(col = Census_Division, lty = race)) +
      facet_wrap( ~ state.reorder2, ncol = 11, drop = F) +
      ylab("Age-standardized mortality rate (per 100,000)") +
      xlab("Year") + 
      ggtitle(paste0("Age-adjusted mortality (per 100,000) in ", sex_i, " for ", cod))# + theme_minimal()
 test

 library(gridExtra)
g <- ggplotGrob(test)
## remove empty panels
g$grobs[names(g$grobs) %in% c("panel-1-1", "panel-1-2")] <- NULL
## remove them from the layout
g$layout <- g$layout[!(g$layout$name %in% c("panel-1-1", "panel-1-2")),]
## move axis closer to panel
#g$layout[g$layout$name == "axis_b-9", c("t", "b")] = c(9,9)

grid.newpage()
grid.draw(g)
```

>>>>

 data.sub <- subset(mortality.rates, sex == "Male" & COD == "Injuries")
 test <- ggplot(data.sub, 
                aes(y = age.std.mortality.rate_med, x = year)) + 
      geom_vline(aes(xintercept = 1983), col = "#636363", lty = 3) +
      geom_vline(aes(xintercept = 1993), col = "#636363", lty = 3) +
      geom_ribbon(aes(ymin = age.std.mortality.rate_LCL, ymax = age.std.mortality.rate_UCL, group = race, fill = Census_Division), col = NA, alpha = 0.5) +
      geom_line(aes(col = Census_Division, lty = race)) +
      facet_wrap( ~ state.reorder2, ncol = 11, drop = F) +
      ylab("Age-standardized mortality rate (per 100,000)") +
      xlab("Year") #+ 
     # ggtitle(paste0("Age-adjusted mortality (per 100,000) in ", sex_i, " for ", cod))# + theme_minimal()
 test

#  library(gridExtra)
# g <- ggplotGrob(test)
# ## remove empty panels
# g$grobs[names(g$grobs) %in% c("panel-1-1", "panel-1-2")] <- NULL
# ## remove them from the layout
# g$layout <- g$layout[!(g$layout$name %in% c("panel-1-1", "panel-1-2")),]
# ## move axis closer to panel
# #g$layout[g$layout$name == "axis_b-9", c("t", "b")] = c(9,9)
# 
# grid.newpage()
# grid.draw(g)
```
